\begin{ThesisAcknowledgments}

I take this opportunity to express my heartfelt gratitude to my supervisors Dr. Vikram Khaire and Dr. Anand Narayanan for their valuable guidance and support throughout the project. I thank Dr. Vikram Khaire for arranging meetings at very unearthly hours also and Dr. Anand Narayanan whose office doors were always open for discussions. I would also like to thank all other faculty members including Dr. Anandmayee Tej, Dr. Samir Mandal, Dr. Jagadheep D, Dr. Resmi L and Dr. Sarita Vig for their invaluable time and making the course-work an enjoyable ride. I also thank Dr. Thomas Shanks for providing us with the valuable data from VIMOS survey.

I am grateful to all my family members including two loving Canis lupus familiaris Jonty and Dom, whose love and consistent support allowed me to withstand all the difficulties and helped me grow and prosper. I am thankful to all my friends, especially Jay, Shriya and Harshit, to create such a fun-filled environment which felt like home away from home and for all the memories which I'll cherish for lifetime. I would also like to thank my seniors Mrs. Surya for extended discussions on learning VPFIT and Mr. Dheeraj to acquaint me with using CLOUDY. 

Last but not the least I would like to thank my psychiatrists Dr. Kumar and Dr. Rashmi, perhaps, without whom I would not have been in a state to continue the course. And I apologise to everyone else whose name is not mentioned or inaptly missed.

\vspace{25mm}

\hfill \Author

\end{ThesisAcknowledgments}
